---
title: "The Effect of Union Membership on Household Income"
author: "Noam Winograd"
date: "2023-02-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())
gc(verbose=FALSE)
```


```{r libraries, echo=FALSE, include=FALSE}
library(haven)
library(data.table)
library(fixest)
library(plotly)
library(dplyr)
library(modi)
library(scales)
library(knitr)
library(kableExtra)

DATA_DIR <-  "C:/Users/user/Documents/labor_eco/final_project"

COUNTRY_CODES_PATH <- file.path(DATA_DIR, 'cow_country_codes.csv')
IVS_PATH <- file.path(DATA_DIR, 'Integrated_values_surveys_1981-2021.dta')

```

# Data Loading and Setup

```{r country codes}
country_codes <- unique(data.table(read.csv(COUNTRY_CODES_PATH)))
colnames(country_codes) <- c("country_short_name", "COW_NUM", "country_name")
country_codes
```

```{r original data}
original_dt <- data.table(read_dta(IVS_PATH))
dt <- merge(original_dt, country_codes, by="COW_NUM")
```

```{r}
load(file="dt")
```

```{r}
mini_dt <- subset(dt, select = c(
  S002, # wave
  S002EVS,
  stdyno_w, #Study number (wave)
  S020, # Year survey
  S024, #Country - wave
  country_name,
  S001, #study
  version,
  doi #EVS/WVS identifier,
  )
                  )
mini_dt <- mini_dt[, wvs_wave_obs_count := .N, by=.(S002)]
obs_from_evs <- unique(mini_dt$wvs_wave_obs_count[is.na(mini_dt$S002)])
paste0("The percent of EVS obs: ", sprintf("%.3f%%", (obs_from_evs/ nrow(dt)) * 100))
```


```{r remove countries with too little observations}
rm(mini_dt)
dt <- dt[, country_obs_count := .N, by=.(country_name)]
dt <- dt[country_obs_count > 500]
```


#code

```{r}
save(dt, file='dt')
rm(original_dt)

#so the enviorment will handle all the files-
# memory.limit(50000)
```


```{r split into waves}
WVS_all_waves <- dt[!is.na(S002)]
WVS1 <- WVS_all_waves[S002 == 1]
WVS2 <- WVS_all_waves[S002 == 2]
WVS3 <- WVS_all_waves[S002 == 3]
WVS4 <- WVS_all_waves[S002 == 4]
WVS5 <- WVS_all_waves[S002 == 5]
WVS6 <- WVS_all_waves[S002 == 6]
WVS7 <- WVS_all_waves[S002 == 7]


EVS_all_waves <- dt[!is.na(S002EVS)]
EVS1 <- EVS_all_waves[S002EVS == 1]
EVS2 <- EVS_all_waves[S002EVS == 2]
EVS3 <- EVS_all_waves[S002EVS == 3]
EVS4 <- EVS_all_waves[S002EVS == 4]
EVS5 <- EVS_all_waves[S002EVS == 5]
```

```{r}
wvs_list <- list(WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7, EVS1, EVS2, EVS3, EVS4, EVS5)

nulls_table <- data.frame(matrix(ncol = 12, nrow = 9))
colnames(nulls_table) <- c("WVS1", "WVS2", "WVS3", "WVS4", "WVS5", "WVS6", "WVS7", "EVS1", "EVS2", "EVS3", "EVS4", "EVS5")
rownames(nulls_table) <- c("Full-time employment rate", "Full-time employment obs", "Filled data about education","Filled data about education obs ", "Filled data about age","Filled data about age obs", "Filled data about religion", "Filled data about religion obs", "Total observations")

```

```{r}
  for (i in 1:12) {
    # employed rate
    employed_rows <- wvs_list[[i]][X028 == 1,]
    employed_percent <- sprintf("%.3f%%", nrow(employed_rows) / nrow(wvs_list[[i]])  * 100)
    dt[1,i] <- employed_percent
    
     # employed obs
    dt[2,i] <-  as.numeric(nrow(employed_rows))
   
    # education non-null rate
    education_rows <- wvs_list[[i]][!is.na(X025),]
    education_percent <-  sprintf("%.3f%%", nrow(education_rows) / nrow(wvs_list[[i]])  * 100)
    dt[3,i] <- education_percent
    
    #educ obs
    dt[4,i] <- as.numeric(nrow(education_rows))
    
    # age non-null rate
    age_rows <- wvs_list[[i]][!is.na(X003),]
    age_percent <- sprintf("%.3f%%", nrow(age_rows) / nrow(wvs_list[[i]]) * 100)
    dt[5,i] <- age_percent
    
    # age non-null obs
    dt[6,i] <- as.numeric(nrow(age_rows))
    
    # religion non-null rate
    religion_rows <- wvs_list[[i]][F034 %in% c(1, 2, 3),]
    religion_percent <- sprintf("%.3f%%", nrow(religion_rows) / nrow(wvs_list[[i]]) * 100)
    dt[7,i] <- religion_percent
    
    # religion non-null obs
    dt[8,i] <- as.numeric(nrow(religion_rows))
    
  }
  
  nulls_table_to_show<-
    nulls_table %>%
    kbl() %>%
    kable_classic(full_width = F, html_font = "Cambria") %>%
    kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
    column_spec(1, bold = T)
  
  nulls_table_to_show

```


```{r basic function}
basic_dt <- function(raw_dt, wvs) {
  # returns the dt with the columns that exists in all waves
  dt <- data.table()
  dt$country <- raw_dt$country_name
  dt$year = raw_dt$S020
  dt$age = raw_dt$X003
  dt$age2 = dt$age * dt$age
  dt$age3 = dt$age * dt$age * dt$age
  dt$weights <- raw_dt$pwght
  dt$male = 1 * (raw_dt$X001 == 1)  # in original data 1 = male, 2 = female. Switching it to 1 = male, 0 = female
  dt$n_children = raw_dt$X011
  dt$employment_status = raw_dt$X028
  dt$marital_status = raw_dt$X007
  dt$religious <- ifelse(dt$F034 %in% c(1,2,3),dt$F034 ,NA)
  dt$educ <- raw_dt$educ
  
  if (wvs) { 
    dt$income <- raw_dt$X047_WVS 
  } else {
    dt$income <- raw_dt$X047_EVS
    dt$union <- raw_dt$A067  # in EVS, all waves have the same parameter
  }
  
  dt
}


number_to_string_education_8_categories <- function(raw_dt) {
#
  raw_dt$X025 <- as.character(raw_dt$X025)
  raw_dt[X025 == "1", X025 := "Primary incomplete"]
  raw_dt[X025 == "2", X025 := "Primary"]
  raw_dt[X025 == "3", X025 := "Secondary technical/vocational incomplete"]
  raw_dt[X025 == "4", X025 := "Secondary technical/vocational"]
  raw_dt[X025 == "5", X025 := "Secondary university preparatory incomplete"]
  raw_dt[X025 == "6", X025 := "Secondary university preparatory"]
  raw_dt[X025 == "7", X025 := "Some university education"]
  raw_dt[X025 == "8", X025 := "University degree"]
     
  raw_dt
}


number_to_string_education_9_categories <- function(raw_dt) {
  # Mapping the numbers to string, this is relevant for WVS wave 7
  
  raw_dt$X025A_01 <- as.character(raw_dt$X025A_01)
  raw_dt[X025A_01 == "0", X025A_01 := "Primary incomplete"]
  raw_dt[X025A_01 == "1", X025A_01 := "Primary"]
  raw_dt[X025A_01 == "2", X025A_01 := "Lower secondary"]
  raw_dt[X025A_01 == "3", X025A_01 := "Upper secondary"]
  raw_dt[X025A_01 == "4", X025A_01 := "Post-secondary non tertiary"]
  raw_dt[X025A_01 == "5", X025A_01 := "Short-cycle tertiary"]
  raw_dt[X025A_01 == "6", X025A_01 := "Bachelor"]
  raw_dt[X025A_01 == "7", X025A_01 := "Master"]
  raw_dt[X025A_01 == "8", X025A_01 := "Doctoral"]

  raw_dt
}

unified_string_to_number_education <- function(raw_dt, categories_col) {
  # unified the string columns back to number
  
  raw_dt[categories_col == "Primary incomplete", educ := "1"]
  
  raw_dt[categories_col %in% c('Primary', 'Secondary technical/vocational incomplete'), educ := "2"]
  
  raw_dt[categories_col %in% c('Secondary technical/vocational', 'Secondary university preparatory incomplete', 'Lower secondary'), educ := "3"]
  
  raw_dt[categories_col %in% c('Secondary university preparatory', 'Upper secondary'), educ := "4"]
  
  raw_dt[categories_col %in% c('Some university education', 'Post-secondary non tertiary', 'Short-cycle tertiary'), educ := "5"]
  
  raw_dt[categories_col %in% c('University degree', 'Bachelor', 'Master', 'Doctoral'), educ := "6"]
  
   raw_dt$educ = as.numeric(raw_dt$educ)
   raw_dt$educ
   
   
  # Meanings:
  # 1 = Less than primary
  # 2 = Primary
  # 3 = Lower secondary (middle school)
  # 4 = upper secondary (high school)
  # 5 = Some university education (no degree)
  # 6 = University Degree
  
}


```




```{r specific WVS functions}
format_WVS1 <- function(raw_dt) {

  raw_dt$educ = NA  # no education in this wave
  raw_dt$union <- raw_dt$A101
  # format religion
  dt <- basic_dt(raw_dt, TRUE)
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  dt
}

format_WVS2 <- function(raw_dt) {
  
  
  raw_dt <- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A067
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_WVS3 <- function(raw_dt) {
  
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A101
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_WVS4 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A067
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_WVS5 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]

  dt
}

format_WVS6 <- function(raw_dt) {
 
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_WVS7 <- function(raw_dt) {
  dt <- basic_dt(raw_dt, TRUE)
  
  # format education
  raw_dt<- number_to_string_education_9_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025A_01 )
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

```


```{r specific EVS functions}
format_EVS1 <- function(raw_dt) {
  dt <- basic_dt(raw_dt, FALSE)
  dt$education = NA  # no education in this wave
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_EVS2 <- function(raw_dt) {
  dt <- basic_dt(raw_dt, FALSE)
  dt$education <- NA # no education in this wave
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_EVS3 <- function(raw_dt) {
  
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
 
  dt <- basic_dt(raw_dt, FALSE)
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
}

format_EVS4 <- function(raw_dt) {
     # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, FALSE)
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}

format_EVS5 <- function(raw_dt) {
 
  
  raw_dt<- number_to_string_education_9_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025A_01 )
  
  dt <- basic_dt(raw_dt, FALSE)
  
  #only if working full time- 
  dt <- dt[employment_status == 1, ]
  
  dt
}
```


```{r format waves}

formatted_WVS1 <- format_WVS1(WVS1)
formatted_WVS2 <- format_WVS2(WVS2)
formatted_WVS3 <- format_WVS3(WVS3)
formatted_WVS4 <- format_WVS4(WVS4)
formatted_WVS5 <- format_WVS5(WVS5)
formatted_WVS6 <- format_WVS6(WVS6)
formatted_WVS7 <- format_WVS7(WVS7)

formatted_EVS1 <- format_EVS1(EVS1)
formatted_EVS2 <- format_EVS2(EVS2)
formatted_EVS3 <- format_EVS3(EVS3)
formatted_EVS4 <- format_EVS4(EVS4)
formatted_EVS5 <- format_EVS5(EVS5)
```
#Checking patterns in result

```{r}

# define a function to calculate the percentage of null education observations
check_null_percent <- function(dt, name, col) {
  dt <- dt[, educ_obs_count := .N, by=.(col)]
  non_NA_educ_count <- unique(dt$educ_obs_count[is.na(col)])
  null_percent <- sprintf("%.3f%%",(non_NA_educ_count / nrow(dt)) * 100)
  c(null_percent, null_percent[1])
}

# apply the check_null_percent function to each dataset
null_percentages <- lapply(list(WVS1, WVS2, WVS3, WVS4, WVS5, WVS6), function(dt){
  check_null_percent(dt, "WVS", dt$X025)
})

formatted_null_percentages <- lapply(list(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7), function(dt){
  check_null_percent(dt, "formatted_WVS", dt$educ)
})


# create a data table to compare the results
educ_compare <- data.table(WVS = paste0("WVS", 1:7),
                         education_nulls_overall_rate = sapply(null_percentages, `[`, 1),
                         Education_nulls_rate_for_full_timers = sapply(formatted_null_percentages, `[`, 2))
educ_compare[7,2] <- check_null_percent(WVS7, "WVS", WVS7$X025A_01)[1]

educ_compare<-
  educ_compare %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T)

educ_compare
```
We can't really see a pattern if people are working full time about their willingness to tell their education level. We can see that in WSV2, WSV4, WSV6, WSV7 people who work full time shared more about their education level, but it's not the case for all waves.


```{r}
rm(EVS1, EVS2, EVS3, EVS4, EVS5, WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7)

```


```{r united formatted waves}
formatted_WVS <- rbind(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, 
                       formatted_WVS7, fill=T)
formatted_EVS <- rbind(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5, fill=T)

formatted_dt <- rbind(formatted_WVS, formatted_EVS, fill=T)

```

```{r}
save(formatted_dt, file="formatted_dt")
```
```{r}
rm(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5)
rm(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7)
```

## Something is weird, the formatted_dt is losing data, we need to check it-

```{r}

check_NAs <- function(col_name, dt){
  nas_rows <- dt[is.na(dt[[col_name]]), ]
  nas_percent <- nrow(nas_rows) / nrow(dt) * 100
  data.frame(col_name = col_name, nas_percent = nas_percent)
}

make_NAs_table <- function(dt){
cols <- colnames(dt)
dt_nas <-  as.data.frame(do.call(rbind, lapply(cols, check_NAs, dt = dt)))

dt_nas_table<-  dt_nas %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T)

print(dt_nas_table)

dt_nas
}

formatted_NAs_df <- make_NAs_table(formatted_dt)
formatted_NAs_WVS1_df <- make_NAs_table(formatted_WVS1)
formatted_NAs_WVS2_df <- make_NAs_table(formatted_WVS2)
```


```{r observation per country}
obs_per_country <- formatted_dt[, .N, by=country]
plot_ly(obs_per_country, x=~country, y=~N, type = 'bar')
```



```{r}
country_data <- formatted_dt[country == "France"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + education + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)
```

## Reggressions and nulls_table
```{r regression function}

regression_function <- function(dt, countries) {
  nulls_table <- list()
  i <- 1
  
  for (co in countries) {
    country_data <- dt[country == co]
    
    # country_data <- country_data[employment_status != 4 &  # retired
    #                              employment_status != 7    # unemployed
    #                             ]
    
    print(paste0(co, " ", nrow(country_data), " "))
    #tryCatch({
    
    #WE NEED TO CLEAR NAS BEFORE THE REG
    
      model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + educ + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
      print(model)
      result <- model$coeftable %>% as.data.frame() %>% head(1) %>% mutate(country=co)
      colnames(result) <- c("Estimate", "sd", "t_value", "pr_t", "country")
      nulls_table[[i]] <- result
      i <- i + 1
   # }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  }
  
  nulls_table <- data.table(bind_rows(nulls_table))
  nulls_table <- nulls_table[order(-Estimate),]
  nulls_table
}

countries <- sort(unique(formatted_dt$country))
nulls_table <- regression_function(formatted_dt, countries)

male_nulls_table <- regression_function(formatted_dt[male == 1,], countries)
female_nulls_table <- regression_function(formatted_dt[male == 0,], countries)

under_age_35_nulls_table <- regression_function(formatted_dt[age <= 35 ,], countries)
over_age_35_nulls_table <- regression_function(formatted_dt[age > 35 ,], countries)

```



```{r plot, echo=FALSE}
plot_ly(nulls_table, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country")

plot_ly(male_nulls_table, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Male")

plot_ly(female_nulls_table, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Female")

plot_ly(under_age_35_nulls_table, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Ages <= 35")

plot_ly(over_age_35_nulls_table, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Ages > 35")
```


```{r AKM country}
#akm_model <- feols(income ~ union + male + age + age2 + age3 + n_children + education  | year + employment_status 
#                   + marital_status + country, data=formatted_dt, weights=~weights, se='hetero')

#fixed_effects_coefs <- fixef(akm_model)

# country
#fe_country <- data.frame(fixed_effects_coefs$country)
#fe_country <- cbind(country = rownames(fe_country), fe_country)

#formatted_dt <- merge(formatted_dt, fe_country, by='country')

#weigted_var_country_fe <- weighted.var(formatted_dt$fixed_effects_coefs.country, formatted_dt$weights, na.rm = T)
#weigted_var_income <- weighted.var(formatted_dt$income, formatted_dt$weights, na.rm = T)

#print(paste0("Variation explained by country fixed effect: ", 
#             100 * round(weigted_var_country_fe / weigted_var_income, 3), "%"))

# if we want, we can do the same to the other fixed effect, and answer the question: 
# "How much of the income variance can be explained by ___?" where ___ can be also year, employment_status, marital_status

```



