---
title: "The Effect of Union Membership on Household Income"
author: "Noam Winograd"
date: "2023-02-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
gc(verbose=FALSE)
```


```{r libraries, echo=FALSE, include=FALSE}
library(haven)
library(data.table)
library(fixest)
library(plotly)
library(dplyr)
library(modi)
library(scales)
library(knitr)
library(kableExtra)
library(tidyverse)
# library(htmltools )
# library(formattable)

DATA_DIR <-  "C:/Users/user/Documents/labor_eco/final_project"
COUNTRY_CODES_PATH <- file.path(DATA_DIR, 'cow_country_codes.csv')
IVS_PATH <- file.path(DATA_DIR, 'Integrated_values_surveys_1981-2021.dta')
```

# Data Loading and Setup

```{r country codes}
country_codes <- unique(data.table(read.csv(COUNTRY_CODES_PATH)))
colnames(country_codes) <- c("country_short_name", "COW_NUM", "country_name")
country_codes
```

```{r}
 unions_data  <- data.table(read_csv("C:/Users/user/Documents/labor_eco/final_project/unions_effect/data-jnKbb.csv"))
colnames(unions_data) <- c("con_code", "country_update","source", "union_rate", "rate_note", "source_note")
europe_contries <- c("AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE")
```

```{r}
paste0("avg worldiwde: ", mean(unions_data$union_rate))
```

```{r}
paste0("avg european countries: ", mean(unions_data$union_rate[unions_data$con_code %in% europe_contries]))
```
```{r}
paste0("avg Israel: ", mean(unions_data$union_rate[unions_data$con_code == "ISR"]))
```


```{r original data}
# original_dt <- data.table(read_dta(IVS_PATH))
# dt <- merge(original_dt, country_codes, by="COW_NUM")
# rm(original_dt)
```

```{r}
load(file="dt")
```

```{r}
mini_dt <- subset(dt, select = c(
  S002, # wave
  S002EVS,
  stdyno_w, #Study number (wave)
  S020, # Year survey
  S024, #Country - wave
  country_name,
  S001, #study
  version,
  doi #EVS/WVS identifier,
  )
                  )
mini_dt <- mini_dt[, wvs_wave_obs_count := .N, by=.(S002)]
obs_from_evs <- unique(mini_dt$wvs_wave_obs_count[is.na(mini_dt$S002)])
paste0("The percent of EVS obs: ", sprintf("%.3f%%", (obs_from_evs/ nrow(dt)) * 100))
```


```{r remove countries with too little observations}
rm(mini_dt)
dt <- dt[, country_obs_count := .N, by=.(country_name)]
dt <- dt[country_obs_count > 500]
```


#code

```{r}
#so the enviorment will handle all the data frames-
memory.limit(50000)
```

```{r}
print_dt <- function(dt){
  dt_to_print <- dt %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T)
  
  print(dt_to_print)
}
```


```{r split into waves}
WVS_all_waves <- dt[!is.na(S002)]
WVS1 <- WVS_all_waves[S002 == 1]
WVS2 <- WVS_all_waves[S002 == 2]
WVS3 <- WVS_all_waves[S002 == 3]
WVS4 <- WVS_all_waves[S002 == 4]
WVS5 <- WVS_all_waves[S002 == 5]
WVS6 <- WVS_all_waves[S002 == 6]
WVS7 <- WVS_all_waves[S002 == 7]
EVS_all_waves <- dt[!is.na(S002EVS)]
EVS1 <- EVS_all_waves[S002EVS == 1]
EVS2 <- EVS_all_waves[S002EVS == 2]
EVS3 <- EVS_all_waves[S002EVS == 3]
EVS4 <- EVS_all_waves[S002EVS == 4]
EVS5 <- EVS_all_waves[S002EVS == 5]
```

# Creating a table will all the relevant nulls

## setting up the table
```{r}
wvs_list <- list(WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7, EVS1, EVS2, EVS3, EVS4, EVS5)
nulls_table <- data.frame(matrix(ncol = 13, nrow = 18))
colnames(nulls_table) <- c("WVS1", "WVS2", "WVS3", "WVS4", "WVS5", "WVS6", "WVS7", "EVS1", "EVS2", "EVS3", "EVS4", "EVS5", "Total observations")
rownames(nulls_table) <- c("Full-time employment rate", "Full-time employment obs", "Filled data about education","Filled education obs ", "Filled data about age","Filled age obs", "Filled data about attachment to religion", "Filled religion obs", "Filled data about union", "Filled union obs", "Filled data about marital status", "Filled marital status obs", "Filled data about children number", "Filled children number obs", "Filled data about income", "Filled income obs", "Assigned weights normalizaion", "Weights normalization filled obs")
```

##  useful tools for later
```{r}
raw_educ_nulls <- c()
raw_income_nulls <- c()
raw_religious_nulls <- c()
raw_employed_nulls <- c()
raw_union_nulls <- c()
raw_age_nulls <- c()
raw_weights_nulls <- c()
raw_marital_status_nulls <- c()
raw_gender_nulls <- c()
raw_n_children_nulls <- c()

beutify_percent <- function(num) {
  sprintf("%.3f%%", num)
}
```

#handling the different fields
```{r}
for (i in 1:12) {
  cur_wave <- wvs_list[[i]]
  row_num <-  nrow(wvs_list[[i]])
  
  # employed rate
  employed_rows <- cur_wave[X028 == 1,]
  employed_percent <- nrow(employed_rows) /row_num  * 100
  raw_employed_nulls[[length(raw_employed_nulls)+1]] = employed_percent 
  nulls_table[1,i] <- beutify_percent(employed_percent)
  # employed obs
  nulls_table[2,i] <-  as.numeric(nrow(employed_rows))

  # education non-null rate
  education_rows <- if (i == 7) cur_wave[!is.na(X025A_01)] else cur_wave[!is.na(X025)]
  education_percent <-  nrow(education_rows) / row_num  * 100
  raw_educ_nulls[[length(raw_educ_nulls)+1]] = education_percent 
  nulls_table[3,i] <- beutify_percent(education_percent)
  #educ obs
  nulls_table[4,i] <- as.numeric(nrow(education_rows))

  
  # age non-null rate
  age_rows <- cur_wave[!is.na(X003),]
  age_percent <- nrow(age_rows) / row_num * 100
  raw_age_nulls[[length(raw_age_nulls)+1]] = age_percent
  nulls_table[5,i] <- beutify_percent(age_percent)
  # age non-null obs
  nulls_table[6,i] <- as.numeric(nrow(age_rows))

  # religion non-null rate
  religion_rows <- cur_wave[F034 %in% c(1, 2, 3),]
  religion_percent <-nrow(religion_rows) / row_num * 100
  raw_religious_nulls[[length(raw_religious_nulls)+1]] = religion_percent
  nulls_table[7,i] <- beutify_percent(religion_percent)
  # religion non-null obs
  nulls_table[8,i] <- as.numeric(nrow(religion_rows))

  # income non-null rate
  union_rows <-
  if (i %in% c(1, 3, 5:7)){
      cur_wave[!is.na(cur_wave$A101),]
    } else {
        cur_wave[!is.na(cur_wave$A067),]
    }
  union_percent <-nrow(union_rows) / row_num * 100
  raw_union_nulls[[length(raw_union_nulls)+1]] = union_percent
  nulls_table[9,i] <- beutify_percent(union_percent)
  # income non-null obs
  nulls_table[10,i] <- as.numeric(nrow(union_rows))

   # marital_status non-null rate
  marital_status_rows <- cur_wave[!is.na(X007),]
  weights_percent <- nrow(marital_status_rows) / row_num * 100
  raw_marital_status_nulls[[length(raw_marital_status_nulls)+1]] = weights_percent
  nulls_table[11,i] <- beutify_percent(weights_percent)
  # marital_status non-null obs
  nulls_table[12,i] <- as.numeric(nrow(marital_status_rows))
  
   # n_children non-null rate
  n_children_rows <- cur_wave[!is.na(X011),]
  n_children_percent <- nrow(n_children_rows) / row_num * 100
  raw_n_children_nulls[[length(raw_n_children_nulls)+1]] = n_children_percent
  nulls_table[13,i] <- beutify_percent(n_children_percent)
  # n_children non-null obs
  nulls_table[14,i] <- as.numeric(nrow(n_children_rows))
  
  # income non-null rate
  income_rows <- 
    if (i %in% c(1:7)){
      cur_wave[!is.na(cur_wave$X047_WVS),]
    } else {
        cur_wave[!is.na(cur_wave$X047_EVS),]
    }
  income_percent <-nrow(income_rows) / row_num * 100
  raw_income_nulls[[length(raw_income_nulls)+1]] = income_percent
  nulls_table[15,i] <- beutify_percent(income_percent)
  # income non-null obs
  nulls_table[16,i] <- as.numeric(nrow(income_rows))
  
  #weights non-null rate
  weights_rows <- cur_wave[!is.na(pwght),]
  weights_percent <- nrow(weights_rows) / row_num * 100
  raw_weights_nulls[[length(raw_weights_nulls)+1]] = weights_percent
  nulls_table[17,i] <- beutify_percent(weights_percent)
  # weights non-null obs
  nulls_table[18,i] <- as.numeric(nrow(weights_rows))
}

# total_obs = c()
# for (i in 1:13){
  
# nulls_table <- nulls_table %>% 
#       mutate(Total = rowSums(across(where(is.numeric))))
```

## Presenting
```{r}
  nulls_table_to_show <- nulls_table %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T) %>%
  # Add alternating row colors
  row_spec(1:2, background = "#B5F8E2") %>%
  row_spec(3:4, background = "#DCF7F9") %>%
  row_spec(5:6, background = "#FCD9DC") %>%
  row_spec(7:8, background = "#BADADE") %>%
  row_spec(9:10, background = "#FFECD6") %>%
  row_spec(11:12, background = "#BFDBED") %>%
  row_spec(13:14, background = "#C1D7CB") %>%
  row_spec(15:16, background = "#CBC7E5") %>%
  row_spec(17:18, background = "#FFFAC2")
nulls_table_to_show # show the formatted table
```



```{r basic function}
basic_dt <- function(raw_dt, wvs) {
  # returns the dt with the columns that exists in all waves
  dt <- data.table()
  dt$country <- raw_dt$country_name
  dt$year = raw_dt$S020
  dt$age = raw_dt$X003
  dt$age2 = dt$age * dt$age
  dt$age3 = dt$age * dt$age * dt$age
  dt$weights <- raw_dt$pwght
  dt$male = 1 * (raw_dt$X001 == 1)  # in original data 1 = male, 2 = female. Switching it to 1 = male, 0 = female
  dt$n_children = raw_dt$X011
  dt$employment_status = raw_dt$X028
  dt$marital_status = raw_dt$X007
  dt$religious <- ifelse(raw_dt$F034 %in% c(1,2,3),raw_dt$F034 ,NA)
  dt$educ <- raw_dt$educ
  
  if (wvs) { 
    dt$income <- raw_dt$X047_WVS 
  } else {
    dt$income <- raw_dt$X047_EVS
    dt$union <- as.numeric(raw_dt$A067)# in EVS, all waves have the same parameter
  }
  
  dt
}
number_to_string_education_8_categories <- function(raw_dt) {
#
  raw_dt$X025 <- as.character(raw_dt$X025)
  raw_dt[X025 == "1", X025 := "Primary incomplete"]
  raw_dt[X025 == "2", X025 := "Primary"]
  raw_dt[X025 == "3", X025 := "Upper Secondary technical/vocational incomplete"] #upper secondary
  raw_dt[X025 == "4", X025 := "Secondary technical/vocational"]
  raw_dt[X025 == "5", X025 := "Secondary university preparatory incomplete"] #we will treat the same as finishing secondary
  raw_dt[X025 == "6", X025 := "Secondary university preparatory"]
  raw_dt[X025 == "7", X025 := "Some university education"]
  raw_dt[X025 == "8", X025 := "University degree"]
     
  raw_dt
}
number_to_string_education_9_categories <- function(raw_dt) {
  # Mapping the numbers to string, this is relevant for WVS wave 7
  
  raw_dt$X025A_01 <- as.character(raw_dt$X025A_01)
  raw_dt[X025A_01 == "0", X025A_01 := "Primary incomplete"]
  raw_dt[X025A_01 == "1", X025A_01 := "Primary"]
  raw_dt[X025A_01 == "2", X025A_01 := "Lower secondary"]
  raw_dt[X025A_01 == "3", X025A_01 := "Upper secondary"]
  raw_dt[X025A_01 == "4", X025A_01 := "Post-secondary non tertiary"]
  raw_dt[X025A_01 == "5", X025A_01 := "Short-cycle tertiary"]
  raw_dt[X025A_01 == "6", X025A_01 := "Bachelor"]
  raw_dt[X025A_01 == "7", X025A_01 := "Master"]
  raw_dt[X025A_01 == "8", X025A_01 := "Doctoral"]
  raw_dt
}
unified_string_to_number_education <- function(raw_dt, categories_col) {
  # unified the string columns back to number
  
  raw_dt[categories_col == "Primary incomplete", educ := "1"]
  
  raw_dt[categories_col %in% c('Primary', 'Upper Secondary technical/vocational incomplete','Lower secondary'), educ := "2"]
  raw_dt[categories_col %in% c('Secondary technical/vocational', 'Secondary university preparatory incomplete'), educ := "3"]
  raw_dt[categories_col %in% c('Secondary university preparatory', 'Upper secondary'), educ := "4"]
  raw_dt[categories_col %in% c('Some university education', 'Post-secondary non tertiary', 'Short-cycle tertiary'), educ := "5"]
  raw_dt[categories_col %in% c('University degree', 'Bachelor', 'Master', 'Doctoral'), educ := "6"]
  
   raw_dt$educ = as.numeric(raw_dt$educ)
   raw_dt$educ
   
   
  # Meanings:
  # 1 = Less than primary
  # 2 = Primary
  # 3 = middle school and high school
  # 4 = post high school courses (13 grade, extra proffesional course)
  # 5 = Some university education (no degree)
  # 6 = University Degree
  
}
```




```{r specific WVS functions}
filter_irrelvant_data <- function(raw_dt){
   #only if working full time- 
  raw_dt <- raw_dt[employment_status == 1, ]
  #only working age
  raw_dt<-raw_dt[age >= 16 & age <= 66,]
  raw_dt
}
format_WVS1 <- function(raw_dt) {
  raw_dt$educ = NA  # no education in this wave
  dt  <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS2 <- function(raw_dt) {
  
  
  raw_dt <- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- as.numeric(raw_dt$A067)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS3 <- function(raw_dt) {
  
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS4 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- as.numeric(raw_dt$A067)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS5 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  dt
}
format_WVS6 <- function(raw_dt) {
 
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS7 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_9_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025A_01 )
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
```




```{r specific EVS functions}
format_EVS1 <- function(raw_dt) {
  dt1 <- basic_dt(raw_dt, FALSE)
  dt1$educ = NA  # no education in this wave
  filter_irrelvant_data(dt1)
  
  dt1
}
format_EVS2 <- function(raw_dt) {
  dt <- basic_dt(raw_dt, FALSE)
  dt$educ <- NA # no education in this wave
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_EVS3 <- function(raw_dt) {
  
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
 
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
}
format_EVS4 <- function(raw_dt) {
     # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_EVS5 <- function(raw_dt) {
 
  
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
```

```{r format waves}
formatted_WVS1 <- format_WVS1(WVS1)
formatted_WVS2 <- format_WVS2(WVS2)
formatted_WVS3 <- format_WVS3(WVS3)
formatted_WVS4 <- format_WVS4(WVS4)
formatted_WVS5 <- format_WVS5(WVS5)
formatted_WVS6 <- format_WVS6(WVS6)
formatted_WVS7 <- format_WVS7(WVS7)
formatted_EVS1 <- format_EVS1(EVS1)
formatted_EVS2 <- format_EVS2(EVS2)
formatted_EVS3 <- format_EVS3(EVS3)
formatted_EVS4 <- format_EVS4(EVS4)
formatted_EVS5 <- format_EVS5(EVS5)
```

#Checking patterns in result

## creating functions to check nulls in data
```{r}
raw_waves <- list(
        formatted_WVS1,
        formatted_WVS2,
        formatted_WVS3,
        formatted_WVS4,
        formatted_WVS5,
        formatted_WVS6,
        formatted_WVS7,
        formatted_EVS1,
        formatted_EVS2,
        formatted_EVS3,
        formatted_EVS4,
        formatted_EVS5
  )
formatted_waves <- list(
    WVS1,
    WVS2,
    WVS3,
    WVS4,
    WVS5,
    WVS6, 
    WVS7,
    EVS1,
    EVS2,
    EVS3,
    EVS4,
    EVS5
  )
```


```{r}
# define a function to calculate the percentage of null education observations
check_null_percent <- function(dt, col) {
  non_nas_rows <- nrow(dt[!is.na(dt[[col]]), ])
  non_nas_percent <- non_nas_rows / nrow(dt) * 100
  non_nas_percent_display <- beutify_percent(non_nas_percent)
  non_nas_percent_display
}

```

#check education

```{r}
# apply the check_null_percent function to each dataset
# educ_non_null_percentages <- lapply(formatted_waves,function(dt){check_null_percent(dt, "X025")})

educ_formatted_non_null_percentages <- lapply(raw_waves,function(dt){check_null_percent(dt, "educ")})

educ_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5)),
  education_non_nulls_rate = lapply(raw_educ_nulls, beutify_percent), 
  Education_non_nulls_rate_after_cleaning = educ_formatted_non_null_percentages)

# Print the updated table
print_dt(educ_compare)


 save(educ_compare, file="educ_compare")
```

#check union
```{r}
union_formatted_non_null_percentages <- lapply(raw_waves,function(dt){check_null_percent(dt, "union")})

union_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5)),
  union_non_nulls_rate = lapply(raw_union_nulls, beutify_percent), 
  union_non_nulls_rate_after_cleaning = union_formatted_non_null_percentages)

# Print the updated table
print_dt(union_compare)


#save(union_compare, file="union_compare")
```

#check marital_status 
```{r}
marital_status_formatted_non_null_percentages <- lapply(raw_waves,function(dt){check_null_percent(dt, "marital_status")})

marital_status_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5)),
  marital_status_non_nulls_rate = lapply(raw_marital_status_nulls, beutify_percent), 
  marital_status_non_nulls_rate_after_cleaning = marital_status_formatted_non_null_percentages)

# Print the updated table
print_dt(marital_status_compare)

```
We can actually see that full-timers are more willing to answer about their marital status.


```{r}
# rm(EVS1, EVS2, EVS3, EVS4, EVS5, WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7)
```


```{r united formatted waves}
formatted_WVS <- rbind(formatted_WVS1,
                       formatted_WVS2,
                       formatted_WVS3,
                       formatted_WVS4,
                       formatted_WVS5,
                       formatted_WVS6,
                       formatted_WVS7,
                       fill=T)
formatted_EVS <- rbind(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5, fill=T)
formatted_dt <- rbind(formatted_WVS, formatted_EVS, fill=T)
```

```{r}
# save(formatted_dt, file="formatted_dt")
```
```{r}
# rm(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5)
# rm(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7)
```



```{r}
# check_NAs <- function(col_name, dt){
#   nas_rows <- dt[is.na(dt[[col_name]]), ]
#   nas_percent <- nrow(nas_rows) / nrow(dt) * 100
#   data.frame(col_name = col_name, nas_percent = nas_percent)
# }
# make_NAs_table <- function(dt, dt_name){
# cols <- colnames(dt)
# dt_nas <-  as.data.frame(do.call(rbind, lapply(cols, check_NAs, dt = dt)))
# dt_nas_table<-  dt_nas %>%
#   kbl() %>%
#   kable_classic(full_width = F, html_font = "Cambria") %>%
#   kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
#   column_spec(1, bold = T) %>%
#   add_header_above(c( "NAs Percentage" = 2))
#   
# print(dt_nas_table)
# dt_nas
# }
# formatted_NAs_df <- make_NAs_table(formatted_dt)
# formatted_NAs_WVS1_df <- make_NAs_table(formatted_WVS1)
# formatted_NAs_WVS2_df <- make_NAs_table(formatted_WVS2)
# formatted_NAs_WVS1_df <- make_NAs_table(formatted_WVS1)
```

```{r observation per country}
obs_per_country <- formatted_dt[, .N, by=country]
print(plot_ly(obs_per_country, x=~country, y=~N, type = 'bar'))
```



```{r}
country_data <- formatted_dt[country == "France"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + educ + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)
```
```{r}
country_data <- formatted_dt[country == "Italy"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + educ + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)


function(dt, col) {
  union_rows <- nrow(dt[(dt[["union"]] == 1), ])
  non_nas_percent <- non_nas_rows / nrow(dt) * 100
  non_nas_percent_display <- beutify_percent(non_nas_percent)
  non_nas_percent_display
}

```

```{r}
country_data <- formatted_dt[country == "Sweden"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + educ + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)


function(dt, col) {
  union_rows <- nrow(dt[(dt[["union"]] == 1), ])
  non_nas_percent <- non_nas_rows / nrow(dt) * 100
  non_nas_percent_display <- beutify_percent(non_nas_percent)
  non_nas_percent_display
}

```
## Reggressions and nulls_table

```{r}
neg_list <- c()
```

```{r regression function}
regression_function <- function(dt, countries, neg_lst) {
  results <- list()
  i <- 1
  
  for (co in countries) {
    country_data <- dt[country == co]
    
    # country_data <- country_data[employment_status != 4 &  # retired
    #                              employment_status != 7    # unemployed
    #                             ]
    
    print(paste0(co, " ", nrow(country_data), " "))
    tryCatch({
    
      model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + employment_status + marital_status + educ + n_children, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
      #print(model)
      if(model$coeftable[1,1] <= 0) {
        neg_list[[length(neg_list)+1]] = co 
      }
      result <- model$coeftable %>% as.data.frame() %>% head(1) %>% mutate(country=co)
      colnames(result) <- c("Estimate", "sd", "t_value", "pr_t", "country")
      results[[i]] <- result
      i <- i + 1
   }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  }
  
  results <- data.table(bind_rows(results))
  results <- results[order(-Estimate),]
  results
}
countries <- sort(unique(formatted_dt$country))
results <- regression_function(formatted_dt, countries)
male_results <- regression_function(formatted_dt[male == 1,], countries)
female_results <- regression_function(formatted_dt[male == 0,], countries)
under_age_35_results <- regression_function(formatted_dt[age <= 35 ,], countries)
over_age_35_results <- regression_function(formatted_dt[age > 35 ,], countries)
```



```{r plot, echo=FALSE}
plot_ly(results, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country")
plot_ly(male_results, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Male")
plot_ly(female_results, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Female")
plot_ly(under_age_35_results, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Ages <= 35")
plot_ly(over_age_35_results, x = ~country) %>% 
  add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
  layout(xaxis = list(categoryorder = "total descending", tickvals = ~country), title="Union Premium per Country - Ages > 35")
```


```{r AKM country}
#akm_model <- feols(income ~ union + male + age + age2 + age3 + n_children + education  | year + employment_status 
#                   + marital_status + country, data=formatted_dt, weights=~weights, se='hetero')
#fixed_effects_coefs <- fixef(akm_model)
# country
#fe_country <- data.frame(fixed_effects_coefs$country)
#fe_country <- cbind(country = rownames(fe_country), fe_country)
#formatted_dt <- merge(formatted_dt, fe_country, by='country')
#weigted_var_country_fe <- weighted.var(formatted_dt$fixed_effects_coefs.country, formatted_dt$weights, na.rm = T)
#weigted_var_income <- weighted.var(formatted_dt$income, formatted_dt$weights, na.rm = T)
#print(paste0("Variation explained by country fixed effect: ", 
#             100 * round(weigted_var_country_fe / weigted_var_income, 3), "%"))
# if we want, we can do the same to the other fixed effect, and answer the question: 
# "How much of the income variance can be explained by ___?" where ___ can be also year, employment_status, marital_status
```
