---
title: "The Effect of Union Membership on Household Income"
author: "Noam Winograd"
date: "2023-02-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
gc(verbose=FALSE)
```


```{r libraries, echo=FALSE, include=FALSE}
library(haven)
library(data.table)
library(fixest)
library(plotly)
library(dplyr)
library(modi)
library(scales)
library(knitr)
library(kableExtra)
library(tidyverse)
# library(htmltools )
# library(formattable)

# Inbar:
# DATA_DIR <- "C:/Users/user/Documents/labor_eco/final_project"
# OFFICIAL_UNION_DATA_PATH <- file.path(DATA_DIR, "unions_effect/data-jnKbb.csv")

# Noam:
DATA_DIR <- "/Users/noam/Personal/HUJI/Labor Economics/Final Project/data"
OFFICIAL_UNION_DATA_PATH <- file.path(DATA_DIR, "data-jnKbb.csv")

# both:
COUNTRY_COW_CODES_PATH <- file.path(DATA_DIR, 'cow_country_codes.csv')
COUNTRY_ISO_CODES_PATH <- file.path(DATA_DIR, 'wikipedia-iso-country-codes.csv')
IVS_PATH <- file.path(DATA_DIR, 'Integrated_values_surveys_1981-2021.dta')
```

# useful functions
```{r}
beutify_percent <- function(num) {
  sprintf("%.3f%%", num)
}

print_dt <- function(dt){
  dt_to_print <- dt %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T)
  
  print(dt_to_print)
}

check_null_percent <- function(dt, col) {
  # calculate the percentage of null observation in the col given
  non_nas_rows <- nrow(dt[!is.na(dt[[col]]), ])
  non_nas_percent <- non_nas_rows / nrow(dt) * 100
  non_nas_percent_display <- beutify_percent(non_nas_percent)
  non_nas_percent_display
}
```


# Data Loading and Setup
## Mapping between country code to their names
```{r country codes}
country_cow_codes <- unique(data.table(read.csv(COUNTRY_COW_CODES_PATH)))
colnames(country_cow_codes) <- c("country_short_name", "COW_NUM", "country_name")

country_iso_codes <- unique(data.table(read.csv(COUNTRY_ISO_CODES_PATH)))
country_iso_codes <- country_iso_codes[, .(English.short.name.lower.case, Alpha.3.code)]
colnames(country_iso_codes) <- c("country_name", "country_short_name")
```

## Official union data
```{r}
unions_data  <- data.table(read.csv(OFFICIAL_UNION_DATA_PATH))
colnames(unions_data) <- c("country_short_name", "country_update","source", "union_rate", "rate_note", "source_note")
europe_contries <- c("AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE")
```


```{r}
merged_union_data <- merge(unions_data, country_iso_codes, by='country_short_name', all=T)
merged_union_data <- merged_union_data[, .(country_name, union_rate)]
merged_union_data
```

Some statistics about union membership around the world:
```{r}
print(paste0("Worldiwde Average: ", beutify_percent(mean(unions_data$union_rate))))
print(paste0("European Countries Average: ", beutify_percent(mean(unions_data$union_rate[unions_data$country_short_name %in% europe_contries]))))
print(paste0("Israel Average: ", beutify_percent(mean(unions_data$union_rate[unions_data$country_short_name == "ISR"]))))
```

## IVS data
```{r original data}
original_dt <- data.table(read_dta(IVS_PATH))
dt <- merge(original_dt, country_cow_codes, by="COW_NUM")
rm(original_dt)
```

```{r}
# load(file="dt")
```

```{r}
mini_dt <- subset(dt, select = c(
  S002, # wave
  S002EVS,
  stdyno_w, #Study number (wave)
  S020, # Year survey
  S024, #Country - wave
  country_name,
  S001, #study
  version,
  doi #EVS/WVS identifier,
  )
                  )
mini_dt <- mini_dt[, wvs_wave_obs_count := .N, by=.(S002)]
obs_from_evs <- unique(mini_dt$wvs_wave_obs_count[is.na(mini_dt$S002)])
print(paste0("The percent of EVS obs: ", beutify_percent((obs_from_evs/ nrow(dt)) * 100)))
rm(mini_dt)
```

```{r remove countries with too little observations}
dt <- dt[, country_obs_count := .N, by=.(country_name)]
dt <- dt[country_obs_count > 500]
```


# code
Increasing the memory limit so the session will not terminate:
```{r}
# so the enviorment will handle all the data frames-
# memory.limit(50000)
```

## Splitting the IVS into waves
This is done so it will be easier to format the variables, as the variables names are slightly different from wave to wave.
```{r split into waves}
WVS_all_waves <- dt[!is.na(S002)]
WVS1 <- WVS_all_waves[S002 == 1]
WVS2 <- WVS_all_waves[S002 == 2]
WVS3 <- WVS_all_waves[S002 == 3]
WVS4 <- WVS_all_waves[S002 == 4]
WVS5 <- WVS_all_waves[S002 == 5]
WVS6 <- WVS_all_waves[S002 == 6]
WVS7 <- WVS_all_waves[S002 == 7]
EVS_all_waves <- dt[!is.na(S002EVS)]
EVS1 <- EVS_all_waves[S002EVS == 1]
EVS2 <- EVS_all_waves[S002EVS == 2]
EVS3 <- EVS_all_waves[S002EVS == 3]
EVS4 <- EVS_all_waves[S002EVS == 4]
EVS5 <- EVS_all_waves[S002EVS == 5]
```

# Creating a table will all the relevant nulls
## setting up the table
```{r}
raw_waves <- list(WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7, EVS1, EVS2, EVS3, EVS4, EVS5)
nulls_table <- data.frame(matrix(ncol = 13, nrow = 18))
colnames(nulls_table) <- c("WVS1", "WVS2", "WVS3", "WVS4", "WVS5", "WVS6", "WVS7", "EVS1", "EVS2", "EVS3", "EVS4", "EVS5", "Total")
rownames(nulls_table) <- c("Employment - Filled Data Ratio", 
                           "Employment - Filled Data Obs", 
                           "Education - Filled Data Ratio",  
                           "Education - Filled Data Obs ", 
                           "Age - Filled Data Ratio", 
                           "Age - Filled Data Obs", 
                           "Attachment to Religion - Filled Data Ratio", 
                           "Attachment to Religion - Filled Data Obs", 
                           "Union Membership - Filled Data Ratio", 
                           "Union Membership - Filled Data Obs", 
                           "Marital Status - Filled Data Ratio", 
                           "Marital Status - Filled Data  Obs", 
                           "No. of Children - Filled Data Ratio", 
                           "No. of Children - Filled Data Obs", 
                           "Income - Filled Data Ratio", 
                           "Income - Filled Data Obs", 
                           "Weights Normalizaion Assignment Ratio", 
                           "Weights Normalizaion Assignment Obs")
```

##  useful tools for later
```{r}
raw_educ_nulls <- c()
raw_income_nulls <- c()
raw_religious_nulls <- c()
raw_employment_nulls <- c()
raw_union_nulls <- c()
raw_age_nulls <- c()
raw_weights_nulls <- c()
raw_marital_status_nulls <- c()
raw_gender_nulls <- c()
raw_n_children_nulls <- c()
```

## Creating the nulls table
```{r}
for (i in 1:12) {
  cur_wave <- raw_waves[[i]]
  row_num <-  nrow(cur_wave)
  
  # employment
  employment_rows <- cur_wave[!is.na(X028),]
  employment_percent <- nrow(employment_rows) / row_num * 100
  raw_employment_nulls[[length(raw_employment_nulls)+1]] = employment_percent
  nulls_table[1,i] <- beutify_percent(employment_percent)
  nulls_table[2,i] <- as.numeric(nrow(employment_rows))

  # education
  educ_rows <- if (i == 7) cur_wave[!is.na(X025A_01)] else cur_wave[!is.na(X025)]
  educ_percent <-  nrow(educ_rows) / row_num  * 100
  raw_educ_nulls[[length(raw_educ_nulls)+1]] = educ_percent 
  nulls_table[3,i] <- beutify_percent(educ_percent)
  nulls_table[4,i] <- as.numeric(nrow(educ_rows))

  # age
  age_rows <- cur_wave[!is.na(X003),]
  age_percent <- nrow(age_rows) / row_num * 100
  raw_age_nulls[[length(raw_age_nulls)+1]] = age_percent
  nulls_table[5,i] <- beutify_percent(age_percent)
  nulls_table[6,i] <- as.numeric(nrow(age_rows))

  # religion
  religion_rows <- cur_wave[!is.na(F034),]
  religion_percent <-nrow(religion_rows) / row_num * 100
  raw_religious_nulls[[length(raw_religious_nulls)+1]] = religion_percent
  nulls_table[7,i] <- beutify_percent(religion_percent)
  nulls_table[8,i] <- as.numeric(nrow(religion_rows))

  # union
  union_rows <-
  if (i %in% c(1, 3, 5:7)){
      cur_wave[!is.na(cur_wave$A101),]
    } else {
        cur_wave[!is.na(cur_wave$A067),]
    }
  union_percent <-nrow(union_rows) / row_num * 100
  raw_union_nulls[[length(raw_union_nulls)+1]] = union_percent
  nulls_table[9,i] <- beutify_percent(union_percent)
  nulls_table[10,i] <- as.numeric(nrow(union_rows))

  # marital_status
  marital_status_rows <- cur_wave[!is.na(X007),]
  marital_status_percent <- nrow(marital_status_rows) / row_num * 100
  raw_marital_status_nulls[[length(raw_marital_status_nulls)+1]] = marital_status_percent
  nulls_table[11,i] <- beutify_percent(marital_status_percent)
  nulls_table[12,i] <- as.numeric(nrow(marital_status_rows))
  
  # n_children
  n_children_rows <- cur_wave[!is.na(X011),]
  n_children_percent <- nrow(n_children_rows) / row_num * 100
  raw_n_children_nulls[[length(raw_n_children_nulls)+1]] = n_children_percent
  nulls_table[13,i] <- beutify_percent(n_children_percent)
  nulls_table[14,i] <- as.numeric(nrow(n_children_rows))
  
  # income
  income_rows <- 
    if (i %in% c(1:7)){
      cur_wave[!is.na(cur_wave$X047_WVS),]
    } else {
        cur_wave[!is.na(cur_wave$X047_EVS),]
    }
  income_percent <-nrow(income_rows) / row_num * 100
  raw_income_nulls[[length(raw_income_nulls)+1]] = income_percent
  nulls_table[15,i] <- beutify_percent(income_percent)
  nulls_table[16,i] <- as.numeric(nrow(income_rows))
  
  #weights
  weights_rows <- cur_wave[!is.na(pwght),]
  weights_percent <- nrow(weights_rows) / row_num * 100
  raw_weights_nulls[[length(raw_weights_nulls)+1]] = weights_percent
  nulls_table[17,i] <- beutify_percent(weights_percent)
  nulls_table[18,i] <- as.numeric(nrow(weights_rows))
}
```

## Filling in the total column
```{r}
# add the total column
row_num <- nrow(dt)

# employed
employment_rows <- dt[!is.na(X028),]
employment_percent <- nrow(employment_rows) / row_num * 100
raw_employment_nulls[[length(raw_employment_nulls)+1]] = employment_percent
nulls_table[1,13] <- beutify_percent(employment_percent)
nulls_table[2,13] <- as.numeric(nrow(employment_rows))

# education
educ_rows <- dt[(S002 == 7 & !is.na(X025A_01)) | !is.na(X025)]
educ_percent <-  nrow(educ_rows) / row_num  * 100
raw_educ_nulls[[length(raw_educ_nulls)+1]] = educ_percent
nulls_table[3,13] <- beutify_percent(educ_percent)
nulls_table[4,13] <- as.numeric(nrow(educ_rows))
rm(educ_rows)

# age
age_rows <- dt[!is.na(X003)]
age_percent <- nrow(age_rows) / row_num * 100
raw_age_nulls[[length(raw_age_nulls)+1]] = age_percent
nulls_table[5,13] <- beutify_percent(age_percent)
nulls_table[6,13] <- as.numeric(nrow(age_rows))
rm(age_rows)

# religion
religion_rows <- dt[!is.na(F034),]
religion_percent <-nrow(religion_rows) / row_num * 100
raw_religious_nulls[[length(raw_religious_nulls)+1]] = religion_percent
nulls_table[7,13] <- beutify_percent(religion_percent)
nulls_table[8,13] <- as.numeric(nrow(religion_rows))
rm(religion_rows)

# union
union_rows <- dt[(S002 %in% c(1, 3, 5:7) & !is.na(A101)) | (!is.na(A067)),]
union_percent <-nrow(union_rows) / row_num * 100
raw_union_nulls[[length(raw_union_nulls)+1]] = union_percent
nulls_table[9,13] <- beutify_percent(union_percent)
nulls_table[10,13] <- as.numeric(nrow(union_rows))
rm(union_rows)

# marital_status
marital_status_rows <- dt[!is.na(X007),]
marital_status_percent <- nrow(marital_status_rows) / row_num * 100
raw_marital_status_nulls[[length(raw_marital_status_nulls)+1]] = marital_status_percent
nulls_table[11,13] <- beutify_percent(marital_status_percent)
nulls_table[12,13] <- as.numeric(nrow(marital_status_rows))
rm(marital_status_rows)

# n_children
n_children_rows <- dt[!is.na(X011),]
n_children_percent <- nrow(n_children_rows) / row_num * 100
nulls_table[13,13] <- beutify_percent(n_children_percent)
nulls_table[14,13] <- as.numeric(nrow(n_children_rows))
rm(n_children_rows)

# income
income_rows <- dt[(!is.na(S002) & !is.na(X047_WVS)) | (!is.na(S002EVS) & !is.na(X047_EVS))]
income_percent <-nrow(income_rows) / row_num * 100
raw_income_nulls[[length(raw_income_nulls)+1]] = income_percent
nulls_table[15,13] <- beutify_percent(income_percent)
nulls_table[16,13] <- as.numeric(nrow(income_rows))
rm(income_rows)

#weights
weights_rows <- dt[!is.na(pwght),]
weights_percent <- nrow(weights_rows) / row_num * 100
nulls_table[17,13] <- beutify_percent(weights_percent)
nulls_table[18,13] <- as.numeric(nrow(weights_rows))
rm(weights_rows)
```

## Presenting the null table
```{r}
nulls_table_to_show <- nulls_table %>%
  kbl() %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
  column_spec(1, bold = T) %>%
  # Add alternating row colors
  row_spec(1:2, background = "#B5F8E2") %>%
  row_spec(3:4, background = "#DCF7F9") %>%
  row_spec(5:6, background = "#FCD9DC") %>%
  row_spec(7:8, background = "#BADADE") %>%
  row_spec(9:10, background = "#FFECD6") %>%
  row_spec(11:12, background = "#BFDBED") %>%
  row_spec(13:14, background = "#C1D7CB") %>%
  row_spec(15:16, background = "#CBC7E5") %>%
  row_spec(17:18, background = "#FFFAC2")
nulls_table_to_show # show the formatted table
```


# IVS Data Formatting
```{r basic function}
basic_dt <- function(raw_dt, wvs) {
  # returns the dt with the columns that exists in all waves
  dt <- data.table()
  dt$country <- raw_dt$country_name
  dt$year = raw_dt$S020
  dt$age = raw_dt$X003
  dt$age2 = dt$age * dt$age
  dt$age3 = dt$age * dt$age * dt$age
  dt$weights <- raw_dt$pwght
  dt$male = 1 * (raw_dt$X001 == 1)  # in original data 1 = male, 2 = female. Switching it to 1 = male, 0 = female
  dt$n_children = raw_dt$X011
  dt$employment_status = raw_dt$X028
  dt$marital_status = raw_dt$X007
  dt$religious <- ifelse(raw_dt$F034 %in% c(1,2,3),raw_dt$F034 ,NA)
  dt$educ <- raw_dt$educ
  
  if (wvs) { 
    dt$income <- raw_dt$X047_WVS 
  } else {
    dt$income <- raw_dt$X047_EVS
    dt$union <- as.numeric(raw_dt$A067)# in EVS, all waves have the same parameter
  }
  
  dt
}
number_to_string_education_8_categories <- function(raw_dt) {
#
  raw_dt$X025 <- as.character(raw_dt$X025)
  raw_dt[X025 == "1", X025 := "Primary incomplete"]
  raw_dt[X025 == "2", X025 := "Primary"]
  raw_dt[X025 == "3", X025 := "Upper Secondary technical/vocational incomplete"] #upper secondary
  raw_dt[X025 == "4", X025 := "Secondary technical/vocational"]
  raw_dt[X025 == "5", X025 := "Secondary university preparatory incomplete"] #we will treat the same as finishing secondary
  raw_dt[X025 == "6", X025 := "Secondary university preparatory"]
  raw_dt[X025 == "7", X025 := "Some university education"]
  raw_dt[X025 == "8", X025 := "University degree"]
     
  raw_dt
}
number_to_string_education_9_categories <- function(raw_dt) {
  # Mapping the numbers to string, this is relevant for WVS wave 7
  
  raw_dt$X025A_01 <- as.character(raw_dt$X025A_01)
  raw_dt[X025A_01 == "0", X025A_01 := "Primary incomplete"]
  raw_dt[X025A_01 == "1", X025A_01 := "Primary"]
  raw_dt[X025A_01 == "2", X025A_01 := "Lower secondary"]
  raw_dt[X025A_01 == "3", X025A_01 := "Upper secondary"]
  raw_dt[X025A_01 == "4", X025A_01 := "Post-secondary non tertiary"]
  raw_dt[X025A_01 == "5", X025A_01 := "Short-cycle tertiary"]
  raw_dt[X025A_01 == "6", X025A_01 := "Bachelor"]
  raw_dt[X025A_01 == "7", X025A_01 := "Master"]
  raw_dt[X025A_01 == "8", X025A_01 := "Doctoral"]
  raw_dt
}
unified_string_to_number_education <- function(raw_dt, categories_col) {
  # unified the string columns back to number
  
  raw_dt[categories_col == "Primary incomplete", educ := "1"]
  
  raw_dt[categories_col %in% c('Primary', 'Upper Secondary technical/vocational incomplete','Lower secondary'), educ := "2"]
  raw_dt[categories_col %in% c('Secondary technical/vocational', 'Secondary university preparatory incomplete'), educ := "3"]
  raw_dt[categories_col %in% c('Secondary university preparatory', 'Upper secondary'), educ := "4"]
  raw_dt[categories_col %in% c('Some university education', 'Post-secondary non tertiary', 'Short-cycle tertiary'), educ := "5"]
  raw_dt[categories_col %in% c('University degree', 'Bachelor', 'Master', 'Doctoral'), educ := "6"]
  
   raw_dt$educ = as.numeric(raw_dt$educ)
   raw_dt$educ
   
   
  # Meanings:
  # 1 = Less than primary
  # 2 = Primary
  # 3 = middle school and high school
  # 4 = post high school courses (13 grade, extra professional course)
  # 5 = Some university education (no degree)
  # 6 = University Degree
}
```


```{r specific WVS functions}
filter_irrelvant_data <- function(raw_dt){
   #only if working full time- 
  raw_dt <- raw_dt[employment_status == 1, ]
  #only working age
  raw_dt<-raw_dt[age >= 16 & age <= 66,]
  raw_dt
}
format_WVS1 <- function(raw_dt) {
  raw_dt$educ = NA  # no education in this wave
  dt  <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS2 <- function(raw_dt) {
  
  
  raw_dt <- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- as.numeric(raw_dt$A067)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS3 <- function(raw_dt) {
  
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS4 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- as.numeric(raw_dt$A067)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS5 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  dt
}
format_WVS6 <- function(raw_dt) {
 
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_WVS7 <- function(raw_dt) {
  
  # format education
  raw_dt<- number_to_string_education_9_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025A_01 )
  
  dt <- basic_dt(raw_dt, TRUE)
  
  dt$union <- raw_dt$A101
  dt$union <- as.numeric(dt$union == 2)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
```


```{r specific EVS functions}
format_EVS1 <- function(raw_dt) {
  dt1 <- basic_dt(raw_dt, FALSE)
  dt1$educ = NA  # no education in this wave
  dt1 <- filter_irrelvant_data(dt1)
  
  dt1
}
format_EVS2 <- function(raw_dt) {
  dt <- basic_dt(raw_dt, FALSE)
  dt$educ <- NA # no education in this wave
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_EVS3 <- function(raw_dt) {
  
   # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
 
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
}
format_EVS4 <- function(raw_dt) {
     # format education
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
format_EVS5 <- function(raw_dt) {
 
  
  raw_dt<- number_to_string_education_8_categories(raw_dt)
  raw_dt$educ <- unified_string_to_number_education(raw_dt, raw_dt$X025)
  
  dt <- basic_dt(raw_dt, FALSE)
  dt<- filter_irrelvant_data(dt)
  
  dt
}
```

```{r format waves}
formatted_WVS1 <- format_WVS1(WVS1)
formatted_WVS2 <- format_WVS2(WVS2)
formatted_WVS3 <- format_WVS3(WVS3)
formatted_WVS4 <- format_WVS4(WVS4)
formatted_WVS5 <- format_WVS5(WVS5)
formatted_WVS6 <- format_WVS6(WVS6)
formatted_WVS7 <- format_WVS7(WVS7)
formatted_EVS1 <- format_EVS1(EVS1)
formatted_EVS2 <- format_EVS2(EVS2)
formatted_EVS3 <- format_EVS3(EVS3)
formatted_EVS4 <- format_EVS4(EVS4)
formatted_EVS5 <- format_EVS5(EVS5)

formatted_waves <- list(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7,
                        formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5)
```

```{r united formatted waves}
formatted_WVS <- rbind(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7, fill=T)
formatted_EVS <- rbind(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5, fill=T)
formatted_dt <- rbind(formatted_WVS, formatted_EVS, fill=T)

formatted_waves_with_total <- list(
  formatted_WVS1, formatted_WVS2,formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7,
  formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5, 
  formatted_dt)
```

# Checking patterns in result

## check education after formatting and filtering
```{r}
educ_formatted_non_null_percentages <- lapply(formatted_waves_with_total, function(dt){check_null_percent(dt, "educ")})

educ_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5), 'Total'),
  education_non_nulls_rate = lapply(raw_educ_nulls, beutify_percent), 
  Education_non_nulls_rate_after_cleaning = educ_formatted_non_null_percentages)

# Print the updated table
print_dt(educ_compare)

save(educ_compare, file="educ_compare")
```

## check union after formatting and filtering
```{r}
union_formatted_non_null_percentages <- lapply(formatted_waves_with_total, function(dt){check_null_percent(dt, "union")})

union_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5), 'Total'),
  union_non_nulls_rate = lapply(raw_union_nulls, beutify_percent), 
  union_non_nulls_rate_after_cleaning = union_formatted_non_null_percentages)

print_dt(union_compare)
save(union_compare, file="union_compare")
```

## check mariatl status after formatting and filtering
```{r}
marital_status_formatted_non_null_percentages <- lapply(formatted_waves_with_total, function(dt){check_null_percent(dt, "marital_status")})

marital_status_compare <- data.table(
  Dataset = c(paste0("WVS", 1:7), paste0("EVS", 1:5), 'Total'),
  marital_status_non_nulls_rate = lapply(raw_marital_status_nulls, beutify_percent), 
  marital_status_non_nulls_rate_after_cleaning = marital_status_formatted_non_null_percentages)

# Print the updated table
print_dt(marital_status_compare)
save(union_compare, file="marital_status_compare")
```

```{r}
# rm(EVS1, EVS2, EVS3, EVS4, EVS5, WVS1, WVS2, WVS3, WVS4, WVS5, WVS6, WVS7)
```

```{r}
# save(formatted_dt, file="formatted_dt")
```

```{r}
# rm(formatted_EVS1, formatted_EVS2, formatted_EVS3, formatted_EVS4, formatted_EVS5)
# rm(formatted_WVS1, formatted_WVS2, formatted_WVS3, formatted_WVS4, formatted_WVS5, formatted_WVS6, formatted_WVS7)
```



```{r}
# check_NAs <- function(col_name, dt){
#   nas_rows <- dt[is.na(dt[[col_name]]), ]
#   nas_percent <- nrow(nas_rows) / nrow(dt) * 100
#   data.frame(col_name = col_name, nas_percent = nas_percent)
# }
# make_NAs_table <- function(dt, dt_name){
# cols <- colnames(dt)
# dt_nas <-  as.data.frame(do.call(rbind, lapply(cols, check_NAs, dt = dt)))
# dt_nas_table<-  dt_nas %>%
#   kbl() %>%
#   kable_classic(full_width = F, html_font = "Cambria") %>%
#   kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
#   column_spec(1, bold = T) %>%
#   add_header_above(c( "NAs Percentage" = 2))
#   
# print(dt_nas_table)
# dt_nas
# }
# formatted_NAs_df <- make_NAs_table(formatted_dt)
# formatted_NAs_WVS1_df <- make_NAs_table(formatted_WVS1)
# formatted_NAs_WVS2_df <- make_NAs_table(formatted_WVS2)
# formatted_NAs_WVS1_df <- make_NAs_table(formatted_WVS1)
```

```{r observation per country}
obs_per_country <- formatted_dt[, .N, by=country]
plot_ly(obs_per_country, x=~country, y=~N, type = 'bar') %>% 
  layout(xaxis = list(tickmode='linear'))
```


# Running Regressions
## France
```{r}
country_data <- formatted_dt[country == "France"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + marital_status + educ + n_children + religious, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)
```

## Italy
```{r}
country_data <- formatted_dt[country == "Italy"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + marital_status + educ + n_children + religious, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)

```

## Sweeden
```{r}
country_data <- formatted_dt[country == "Sweden"]
model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + marital_status + educ + n_children + religious, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
print(model)

```

## Reggression function - All countries
```{r regression function}

setFixest_notes(FALSE)
regression_function <- function(dt, countries) {
  results <- list()
  i <- 1
  
  for (co in countries) {
    country_data <- dt[country == co]
    nrow_country_data <- nrow(country_data)
    union_rate_in_dt <- 100 * nrow(country_data[union == 1]) / nrow(country_data[!is.na(union)])
    
    print(paste0(co, " ", nrow(country_data), " "))
    tryCatch({
      model <- feols(income ~ union + male + age + age2 + age3 | 
                       year + marital_status + educ + n_children + religious, 
                     data=country_data, 
                     weights=~weights, 
                     se='hetero')
      result <- model$coeftable %>% as.data.frame() %>% head(1) %>% 
        mutate(country=co, 
               country_n_obs=nrow_country_data, 
               regresion_n_obs=model$nobs,
               union_rate=union_rate_in_dt)
      colnames(result) <- c("Estimate", "sd", "t_value", "pr_t", "country_name", 
                            'country_n_obs', 'regresion_n_obs', 'union_rate_in_data')
      results[[i]] <- result
      i <- i + 1
   }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  }
  
  results <- data.table(bind_rows(results))
  results <- results[order(-Estimate),]
  
  merged_results <- merge(results, merged_union_data, by='country_name', all.x=T)
  merged_results
}

```

```{r}
countries <- sort(unique(formatted_dt$country))
results <- regression_function(formatted_dt, countries)
male_results <- regression_function(formatted_dt[male == 1,], countries)
female_results <- regression_function(formatted_dt[male == 0,], countries)
under_age_35_results <- regression_function(formatted_dt[age <= 35 ,], countries)
over_age_35_results <- regression_function(formatted_dt[age > 35 ,], countries)
uneducated_results <- regression_function(formatted_dt[educ < 6 ,], countries)
educated_results <- regression_function(formatted_dt[educ == 6 ,], countries)

```

## Pretty Tables of the Results
```{r}
pretty_results_table <- function(results, with_official_union=F) {
  results <- results[order(country_name)]
  if (with_official_union) {
    pretty_results <- results
    colnames(pretty_results) <- c("Country", "Union Membership Estimate", "Std. Error", "t value", "Pr(>|t|)", 
                                  "No. Observation", "Reggression No. Observation", 'Union Rate', 'Official Union Rate')  
  } else {
    pretty_results <- results[, .(country_name, Estimate, sd, t_value, pr_t, country_n_obs, regresion_n_obs, union_rate_in_data)]
    colnames(pretty_results) <- c("Country", "Union Membership Estimate", "Std. Error", "t value", "Pr(>|t|)", 
                                  "No. Observation", "Reggression No. Observation", 'Union Rate')  
  }
  
  results_table_to_show <- pretty_results %>%
    kbl() %>%
    kable_classic(full_width = F, html_font = "Cambria") %>%
    kable_styling(bootstrap_options = "striped", full_width = F, font_size = 16) %>%
    column_spec(1, bold = T)
  results_table_to_show  
}

pretty_results_table(results, T)
pretty_results_table(male_results)
pretty_results_table(female_results)
pretty_results_table(under_age_35_results)
pretty_results_table(over_age_35_results)
pretty_results_table(uneducated_results)
pretty_results_table(educated_results)

```


```{r plot, echo=FALSE}
plot_results <- function(results, title) {
  plot <- plot_ly(results, x = ~country_name) %>% 
    add_trace(y = ~Estimate, type = 'scatter', mode='markers', error_y = ~list(array = 1.96 * sd, color='lightblue')) %>% 
    layout(xaxis = list(categoryorder = "total descending", tickvals = ~country_name, title=""), title=title)
  plot
}

plot_results(results, "Union Premium per Country")
plot_results(male_results, "Union Premium per Country - Male")
plot_results(female_results, "Union Premium per Country - Female")
plot_results(under_age_35_results, "Union Premium per Country - Age <= 35")
plot_results(over_age_35_results, "Union Premium per Country - Age > 35")
plot_results(uneducated_results, "Union Premium per Country - Without University Degree")
plot_results(educated_results, "Union Premium per Country - With University Degree")

```


```{r AKM country}
#akm_model <- feols(income ~ union + male + age + age2 + age3 + n_children + education  | year + employment_status 
#                   + marital_status + country, data=formatted_dt, weights=~weights, se='hetero')
#fixed_effects_coefs <- fixef(akm_model)
# country
#fe_country <- data.frame(fixed_effects_coefs$country)
#fe_country <- cbind(country = rownames(fe_country), fe_country)
#formatted_dt <- merge(formatted_dt, fe_country, by='country')
#weigted_var_country_fe <- weighted.var(formatted_dt$fixed_effects_coefs.country, formatted_dt$weights, na.rm = T)
#weigted_var_income <- weighted.var(formatted_dt$income, formatted_dt$weights, na.rm = T)
#print(paste0("Variation explained by country fixed effect: ", 
#             100 * round(weigted_var_country_fe / weigted_var_income, 3), "%"))
# if we want, we can do the same to the other fixed effect, and answer the question: 
# "How much of the income variance can be explained by ___?" where ___ can be also year, employment_status, marital_status
```

